Temporal graph realization from fastest paths

### 2024-03-31 Arxiv-31-3-24/arxiv.tex
added arxiv version

\usepackage{graphicx}
\graphicspath{{../Figures/}}

@@

\bibliography{bibliography}

>>>>

\usepackage{graphicx}
%\graphicspath{{Figures/}}

@@

\begin{thebibliography}{10}

	\bibitem{akrida2017complexity}
	Eleni~C Akrida, Leszek G{\k{a}}sieniec, George~B. Mertzios, and Paul~G
	Spirakis.
	\newblock The complexity of optimal design of temporally connected graphs.
	\newblock {\em Theory of Computing Systems}, 61:907--944, 2017.

	\bibitem{Akrida-explorer-21}
	Eleni~C. Akrida, George~B. Mertzios, Paul~G. Spirakis, and Christoforos
	Raptopoulos.
	\newblock The temporal explorer who returns to the base.
	\newblock {\em Journal of Computer and System Sciences}, 120:179--193, 2021.

	\bibitem{Arrighi2023Multi}
	Emmanuel Arrighi, Niels Gr{\"u}ttemeier, Nils Morawietz, Frank Sommer, and
	Petra Wolf.
	\newblock Multi-parameter analysis of finding minors and subgraphs
	in edge-periodic temporal graphs.
	\newblock In {\em Proceedings of the 48th International Conference on Current
		Trends in Theory and Practice of Computer Science (SOFSEM)}, pages 283--297,
	2023.

	\bibitem{augustine2022distributed}
	John Augustine, Keerti Choudhary, Avi Cohen, David Peleg, Sumathi
	Sivasubramaniam, and Suman Sourav.
	\newblock Distributed graph realizations.
	\newblock {\em IEEE Transactions on Parallel and Distributed Systems},
	33(6):1321--1337, 2022.

	\bibitem{barNoy2020efficiently}
	Amotz Bar{-}Noy, Keerti Choudhary, David Peleg, and Dror Rawitz.
	\newblock Efficiently realizing interval sequences.
	\newblock {\em SIAM Journal on Discrete Mathematics}, 34(4):2318--2337, 2020.

	\bibitem{Bar-NoyCPR20}
	Amotz Bar{-}Noy, Keerti Choudhary, David Peleg, and Dror Rawitz.
	\newblock Graph realizations: Maximum degree in vertex neighborhoods.
	\newblock In {\em Proceedings of the 17th Scandinavian Symposium and Workshops
		on Algorithm Theory (SWAT)}, pages 10:1--10:17, 2020.

	\bibitem{barNoy2021composed}
	Amotz Bar{-}Noy, David Peleg, Mor Perry, and Dror Rawitz.
	\newblock Composed degree-distance realizations of graphs.
	\newblock In {\em Proceedings of the 32nd International Workshop on
		Combinatorial Algorithms ({IWOCA})}, pages 63--77, 2021.

	\bibitem{barNoy2022GraphRealization}
	Amotz Bar-Noy, David Peleg, Mor Perry, and Dror Rawitz.
	\newblock Graph realization of distance sets.
	\newblock In {\em Proceedings of the 47th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, pages 13:1--13:14,
	2022.

	\bibitem{behzad1976eccentric}
	Mehdi Behzad and James~E Simpson.
	\newblock Eccentric sequences and eccentric sets in graphs.
	\newblock {\em Discrete Mathematics}, 16(3):187--193, 1976.

	\bibitem{bixby1988almost}
	Robert~E Bixby and Donald~K Wagner.
	\newblock An almost linear-time algorithm for graph realization.
	\newblock {\em Mathematics of Operations Research}, 13(1):99--123, 1988.

	\bibitem{xuan_computing_2003}
	Binh-Minh Bui-Xuan, Afonso Ferreira, and Aubin Jarry.
	\newblock Computing shortest, fastest, and foremost journeys in dynamic
	networks.
	\newblock {\em International Journal of Foundations of Computer Science},
	14(02):267--285, 2003.

	\bibitem{CasteigtsCS22}
	Arnaud Casteigts, Timoth{\'{e}}e Corsini, and Writika Sarkar.
	\newblock Invited paper: Simple, strict, proper, happy: A study of reachability
	in temporal graphs.
	\newblock In {\em Proceedings of the 24th International Symposium on
		Stabilization, Safety, and Security of Distributed Systems ({SSS})}, pages
	3--18, 2022.

	\bibitem{casteigts2012time}
	Arnaud Casteigts, Paola Flocchini, Walter Quattrociocchi, and Nicola Santoro.
	\newblock Time-varying graphs and dynamic networks.
	\newblock {\em International Journal of Parallel, Emergent and Distributed
		Systems}, 27(5):387--408, 2012.

	\bibitem{casteigts2021finding}
	Arnaud Casteigts, Anne-Sophie Himmel, Hendrik Molter, and Philipp Zschoche.
	\newblock Finding temporal paths under waiting time constraints.
	\newblock {\em Algorithmica}, 83(9):2754--2802, 2021.

	\bibitem{chen1966realization}
	Wai-Kai Chen.
	\newblock On the realization of a $(p, s)$-digraph with prescribed degrees.
	\newblock {\em Journal of the Franklin Institute}, 281(5):406--422, 1966.

	\bibitem{chung2001distance}
	Fan Chung, Mark Garrett, Ronald Graham, and David Shallcross.
	\newblock Distance realization problems with applications to internet
	tomography.
	\newblock {\em Journal of Computer and System Sciences}, 63(3):432--448, 2001.

	\bibitem{culberson1989fast}
	Joseph~C. Culberson and Piotr Rudnicki.
	\newblock A fast algorithm for constructing trees from distance matrices.
	\newblock {\em Information Processing Letters}, 30(4):215--220, 1989.

	\bibitem{Cyg+15}
	Marek Cygan, Fedor~V. Fomin, {\L{}}ukasz Kowalik, Daniel Lokshtanov,
	D{\'{a}}niel Marx, Marcin Pilipczuk, Micha\l{} Pilipczuk, and Saket Saurabh.
	\newblock {\em Parameterized Algorithms}.
	\newblock Springer, 2015.

	\bibitem{deligkas2022optimizing}
	Argyrios Deligkas and Igor Potapov.
	\newblock Optimizing reachability sets in temporal graphs by delaying.
	\newblock {\em Information and Computation}, 285:104890, 2022.

	\bibitem{DF13}
	Rodney~G. Downey and Michael~R. Fellows.
	\newblock {\em Fundamentals of Parameterized Complexity}.
	\newblock Texts in Computer Science. Springer, London, 2013.

	\bibitem{enright2021deleting}
	Jessica Enright, Kitty Meeks, George~B. Mertzios, and Viktor Zamaraev.
	\newblock Deleting edges to restrict the size of an epidemic in temporal
	networks.
	\newblock {\em Journal of Computer and System Sciences}, 119:60--77, 2021.

	\bibitem{enright2021assigning}
	Jessica Enright, Kitty Meeks, and Fiona Skerman.
	\newblock Assigning times to minimise reachability in temporal graphs.
	\newblock {\em Journal of Computer and System Sciences}, 115:169--186, 2021.

	\bibitem{EMM22}
	Jessica~A. Enright, Kitty Meeks, and Hendrik Molter.
	\newblock Counting temporal paths.
	\newblock In {\em Proceedings of the 40th International Symposium on
		Theoretical Aspects of Computer Science ({STACS})}, volume 254, pages
	30:1--30:19, 2023.

	\bibitem{erdos1960graphs}
	Paul Erd{\H{o}}s and Tibor Gallai.
	\newblock Graphs with prescribed degrees of vertices.
	\newblock {\em Mat. Lapok}, 11:264--274, 1960.

	\bibitem{erlebach2021temporal}
	Thomas Erlebach, Michael Hoffmann, and Frank Kammer.
	\newblock On temporal graph exploration.
	\newblock {\em Journal of Computer and System Sciences}, 119:1--18, 2021.

	\bibitem{ErlebachMW-SAND24}
	Thomas Erlebach, Nils Morawietz, and Petra Wolf.
	\newblock Parameterized algorithms for multi-label periodic temporal graph
	realization.
	\newblock In {\em Proceedings of the 3rd Symposium on Algorithmic Foundations
		of Dynamic Networks ({SAND})}, pages 14:1--14:16, 2024.
	\newblock \href {https://doi.org/10.4230/LIPIcs.SAND.2024.14}
	{\path{doi:10.4230/LIPIcs.SAND.2024.14}}.

	\bibitem{ErlebachS20}
	Thomas Erlebach and Jakob~T. Spooner.
	\newblock A game of cops and robbers on graphs with periodic edge-connectivity.
	\newblock In {\em Proceedings of the 46th International Conference on Current
		Trends in Theory and Practice of Informatics (SOFSEM)}, pages 64--75, 2020.

	\bibitem{fellows2009multipleinterval}
	Michael~R. Fellows, Danny Hermelin, Frances Rosamond, and St{\'e}phane
	Vialette.
	\newblock On the parameterized complexity of multiple-interval graph problems.
	\newblock {\em Theoretical Computer Science}, 410(1):53--61, 2009.

	\bibitem{FJR13}
	Michael~R. Fellows, Bart M.~P. Jansen, and Frances~A. Rosamond.
	\newblock Towards fully multivariate algorithmics: {P}arameter ecology and the
	deconstruction of computational complexity.
	\newblock {\em European Journal of Combinatorics}, 34(3):541--566, 2013.

	\bibitem{FG06}
	J{\"o}rg Flum and Martin Grohe.
	\newblock {\em Parameterized Complexity Theory}, volume XIV of {\em Texts in
		Theoretical Computer Science. An EATCS Series}.
	\newblock Springer, 2006.

	\bibitem{Flu+19a}
	Till Fluschnik, Hendrik Molter, Rolf Niedermeier, Malte Renken, and Philipp
	Zschoche.
	\newblock Temporal graph classes: A view through temporal separators.
	\newblock {\em Theoretical Computer Science}, 806:197--218, 2020.

	\bibitem{frank1992augmenting}
	Andr{\'a}s Frank.
	\newblock Augmenting graphs to meet edge-connectivity requirements.
	\newblock {\em SIAM Journal on Discrete Mathematics}, 5(1):25--53, 1992.

	\bibitem{frank1994connectivity}
	Andr{\'a}s Frank.
	\newblock Connectivity augmentation problems in network design.
	\newblock {\em Mathematical Programming: State of the Art 1994}, 1994.

	\bibitem{frank1970connectivity}
	H.~Frank and Wushow Chou.
	\newblock Connectivity considerations in the design of survivable networks.
	\newblock {\em IEEE Transactions on Circuit Theory}, 17(4):486--490, 1970.

	\bibitem{FMNR22a}
	Eugen F\"uchsle, Hendrik Molter, Rolf Niedermeier, and Malte Renken.
	\newblock Delay-robust routes in temporal graphs.
	\newblock In {\em Proceedings of the 39th International Symposium on
		Theoretical Aspects of Computer Science (STACS)}, pages 30:1--30:15, 2022.

	\bibitem{FuchsleMNR22}
	Eugen F{\"{u}}chsle, Hendrik Molter, Rolf Niedermeier, and Malte Renken.
	\newblock Temporal connectivity: Coping with foreseen and unforeseen delays.
	\newblock In {\em Proceedings of the 1st Symposium on Algorithmic Foundations
		of Dynamic Networks ({SAND})}, pages 17:1--17:17, 2022.

	\bibitem{fulkerson1960zero}
	D.R. Fulkerson.
	\newblock Zero-one matrices with zero trace.
	\newblock {\em Pacific Journal of Mathematics}, 10(3):831--836, 1960.

	\bibitem{GolovachM17}
	Petr~A. Golovach and George~B. Mertzios.
	\newblock Graph editing to a given degree sequence.
	\newblock {\em Theoretical Computer Science}, 665:1--12, 2017.

	\bibitem{GolumbicTrenk04}
	Martin~Charles Golumbic and Ann~N. Trenk.
	\newblock {\em Tolerance Graphs}.
	\newblock Cambridge Studies in Advanced Mathematics. Cambridge University
	Press, 2004.

	\bibitem{gomory1961multi}
	Ralph~E Gomory and Tien~Chung Hu.
	\newblock Multi-terminal network flows.
	\newblock {\em Journal of the Society for Industrial and Applied Mathematics},
	9(4):551--570, 1961.

	\bibitem{grotschel1995design}
	Martin Gr{\"o}tschel, Clyde~L Monma, and Mechthild Stoer.
	\newblock Design of survivable networks.
	\newblock {\em Handbooks in Operations Research and Management Science},
	7:617--672, 1995.

	\bibitem{GHN04}
	Jiong Guo, Falk H{\"u}ffner, and Rolf Niedermeier.
	\newblock A structural view on parameterizing problems: Distance from
	triviality.
	\newblock In {\em Proceedings of the 1st International Workshop on
		Parameterized and Exact Computation (IWPEC)}, pages 162--173, 2004.

	\bibitem{hakimi1962realizability}
	S.~Louis Hakimi.
	\newblock On realizability of a set of integers as degrees of the vertices of a
	linear graph.~{I}.
	\newblock {\em Journal of the Society for Industrial and Applied Mathematics},
	10(3):496--506, 1962.

	\bibitem{hakimi1965distance}
	S.~Louis Hakimi and Stephen~S. Yau.
	\newblock Distance matrix of a graph and its realizability.
	\newblock {\em Quarterly of applied mathematics}, 22(4):305--317, 1965.

	\bibitem{hell2009linear}
	Pavol Hell and David Kirkpatrick.
	\newblock Linear-time certifying algorithms for near-graphical sequences.
	\newblock {\em Discrete Mathematics}, 309(18):5703--5713, 2009.

	\bibitem{KKK00}
	David Kempe, Jon~M. Kleinberg, and Amit Kumar.
	\newblock Connectivity and inference problems for temporal networks.
	\newblock {\em Journal of Computer and System Sciences}, 64(4):820--842, 2002.

	\bibitem{klobas2023interference}
	Nina Klobas, George~B. Mertzios, Hendrik Molter, Rolf Niedermeier, and Philipp
	Zschoche.
	\newblock Interference-free walks in time: Temporally disjoint paths.
	\newblock {\em Autonomous Agents and Multi-Agent Systems}, 37(1):1, 2023.

	\bibitem{KlobasMMS22}
	Nina Klobas, George~B. Mertzios, Hendrik Molter, and Paul~G. Spirakis.
	\newblock The complexity of computing optimum labelings for temporal
	connectivity.
	\newblock In {\em Proceedings of the 47th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, pages 62:1--62:15,
	2022.

	\bibitem{Kuhn2011Dynamic}
	Fabian Kuhn and Rotem Oshman.
	\newblock Dynamic networks: Models and algorithms.
	\newblock {\em SIGACT News}, 42(1):82–96, mar 2011.

	\bibitem{Lenstra1983Integer}
	Hendrik~W. Lenstra.
	\newblock Integer programming with a fixed number of variables.
	\newblock {\em Mathematics of Operations Research}, 8:538--548, 1983.

	\bibitem{snapnets}
	Jure Leskovec and Andrej Krevl.
	\newblock {SNAP Datasets}: {Stanford} large network dataset collection.
	\newblock \url{http://snap.stanford.edu/data}, June 2014.

	\bibitem{lesniak1975eccentric}
	Linda Lesniak.
	\newblock Eccentric sequences in graphs.
	\newblock {\em Periodica Mathematica Hungarica}, 6:287--293, 1975.

	\bibitem{McConnellS02}
	Ross~M. McConnell and Jeremy~P. Spinrad.
	\newblock Construction of probe interval models.
	\newblock In {\em Proceedings of the 13th Annual {ACM-SIAM} Symposium on
		Discrete Algorithms (SODA)}, pages 866--875, 2002.

	\bibitem{McMorris98}
	F.R. McMorris, Chi Wang, and Peisen Zhang.
	\newblock On probe interval graphs.
	\newblock {\em Discrete Applied Mathematics}, 88(1):315--324, 1998.
	\newblock Computational Molecular Biology DAM - CMB Series.

	\bibitem{MertziosMS19}
	George~B. Mertzios, Othon Michail, and Paul~G. Spirakis.
	\newblock Temporal network optimization subject to connectivity constraints.
	\newblock {\em Algorithmica}, 81(4):1416--1449, 2019.

	\bibitem{Mertzios-transitivity21}
	George~B. Mertzios, Hendrik Molter, Malte Renken, Paul~G. Spirakis, and Philipp
	Zschoche.
	\newblock The complexity of transitively orienting temporal graphs.
	\newblock In {\em Proceedings of the 46th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, pages 75:1--75:18,
	2021.

	\bibitem{MMS24}
	George~B. Mertzios, Hendrik Molter, and Paul~G. Spirakis.
	\newblock Realizing temporal transportation trees.
	\newblock {\em CoRR}, abs/2403.18513, 2024.
	\newblock URL: \url{https://doi.org/10.48550/arXiv.2403.18513}, \href
	{http://arxiv.org/abs/2403.18513} {\path{arXiv:2403.18513}}.

	\bibitem{MolterRZ21}
	Hendrik Molter, Malte Renken, and Philipp Zschoche.
	\newblock Temporal reachability minimization: Delaying vs. deleting.
	\newblock In {\em Proceedings of the 46th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, pages 76:1--76:15,
	2021.

	\bibitem{morawietz2020timecop}
	Nils Morawietz, Carolin Rehs, and Mathias Weller.
	\newblock A timecop's work is harder than you think.
	\newblock In {\em Proceedings of the 45th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, volume 170, pages
	71--1, 2020.

	\bibitem{morawietz2021timecop}
	Nils Morawietz and Petra Wolf.
	\newblock A timecop’s chase around the table.
	\newblock In {\em Proceedings of the 46th International Symposium on
		Mathematical Foundations of Computer Science (MFCS)}, 2021.

	\bibitem{Patrinos-Hakimi-72}
	A.N. Patrinos and S.~Louis Hakimi.
	\newblock The distance matrix of a graph and its tree realization.
	\newblock {\em Quarterly of Applied Mathematics}, 30:255--269, 1972.

	\bibitem{Rubei16}
	Elena Rubei.
	\newblock Weighted graphs with distances in given ranges.
	\newblock {\em Journal of Classification}, 33:282–--297, 2016.

	\bibitem{sapiezynski2015tracking}
	Piotr Sapiezynski, Arkadiusz Stopczynski, Radu Gatej, and Sune Lehmann.
	\newblock Tracking human mobility using wifi signals.
	\newblock {\em PloS one}, 10(7):e0130824, 2015.

	\bibitem{Schaefer1978complexity}
	Thomas~J. Schaefer.
	\newblock The complexity of satisfiability problems.
	\newblock In {\em Proceedings of the 10th Annual {ACM} Symposium on Theory of
		Computing (STOC)}, pages 216--226, 1978.

	\bibitem{Tamura93}
	H.~Tamura, M.~Sengoku, S.~Shinoda, and T.~Abe.
	\newblock Realization of a network from the upper and lower bounds of the
	distances (or capacities) between vertices.
	\newblock In {\em Proceedings of the 1993 IEEE International Symposium on
		Circuits and Systems (ISCAS)}, pages 2545–--2548, 1993.

	\bibitem{Wu2016Efficient}
	Huanhuan Wu, James Cheng, Yiping Ke, Silu Huang, Yuzhen Huang, and Hejun Wu.
	\newblock Efficient algorithms for temporal path computation.
	\newblock {\em {IEEE} Transactions on Knowledge and Data Engineering},
	28(11):2927--2942, 2016.

	\bibitem{Zsc+19}
	Philipp Zschoche, Till Fluschnik, Hendrik Molter, and Rolf Niedermeier.
	\newblock The complexity of finding separators in temporal graphs.
	\newblock {\em Journal of Computer and System Sciences}, 107:72--92, 2020.

\end{thebibliography}
